Title here

### 2016-12-12 portfolio/text/ms.Rmd
Fix caption

\caption{Effect of specializing on year-to-year changes in revenue and revenue
variability for individual permit holders \emph{within} the `r nstr` most common
strategies. Changing species diversity from year-to-year is associated with
higher variability for individuals within the strategies above the zero line.
Specializing is associated with greater expected revenue to the right of the
zero line and lower expected revenue to the left of the zero line. For example,
individuals with setnet permits for salmon in Prince William Sound, Cook Inlet,
Kodiak, Bristol Bay, or the Alaska Peninsula target primarily sockeye salmon and
experience a $\sim$1.5\% increase in their year-to-year revenue ratio for a 1\%
decrease in their year-to-year species diversity. These effects are estimated
holding fishing season length constant from year-to-year. Dots and line segments
represent medians and 50\% credible intervals of posteriors. The effect of
generalizing (increasing species diversity) is similar (Fig. S\ref{fig:mirror})}.

>>>>

\caption{Effect of specializing on year-to-year changes in revenue and revenue
variability for individual permit holders \emph{within} the `r nstr` most common
strategies. Changing species diversity from year-to-year is associated with
higher variability for individuals within the strategies above the zero line.
Specializing is associated with greater expected revenue ratios to the right of
the zero line and lower expected revenue ratios to the left of the zero line.
For example, individuals with setnet permits for salmon in Prince William Sound,
Cook Inlet, Kodiak, Bristol Bay, or the Alaska Peninsula (second purple dot from
right) target primarily sockeye salmon and experience a $\sim$1.5\% increase in
their year-to-year revenue ratio (horizontal axis) and a $\sim$0.5\% increase in
their revenue variability (vertical axis) for a 1\% decrease in their ratio of
year-to-year species diversity. These effects are estimated holding fishing
season length constant from year-to-year. Dots and line segments represent
medians and 50\% credible intervals of posteriors. The effect of generalizing
(increasing species diversity) is similar (Fig. S\ref{fig:mirror}).}
